DNest4: An implementation of Diffusive Nested Sampling in C++11 and Python

### 2016-05-10 paper/ms.tex
Fixed bibliography
minted

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}

@@

@@

\begin{thebibliography}{99}
\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
arXiv:0808.0012.

@@

\begin{thebibliography}{999}
\end{thebibliography}

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{dsfont}
\usepackage{minted}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}

@@

\begin{minted}[mathescape,
               numbersep=5pt,
               gobble=0,
               frame=single,
               framesep=2mm, fontsize=\small]{c++}
void StraightLine::from_prior(RNG& rng)
{
    // Naive diffuse prior
    m = 1E3*rng.randn();
    b = 1E3*rng.randn();

    // Log-uniform prior
    sigma = exp(-10. + 20.*rng.rand());

    // Compute the model line
    calculate_mu();
}
\end{minted}

\begin{minted}[mathescape,
               numbersep=5pt,
               gobble=0,
               frame=single,
               framesep=2mm, fontsize=\small]{c++}
double StraightLine::perturb(RNG& rng)
{
    double log_H = 0.;

    // Proposals explore the prior
    // For normal priors I usually use the hastings factor to do it
    int which = rng.rand_int(3);
    if(which == 0)
    {
        log_H -= -0.5*pow(m/1E3, 2);
        m += 1E3*rng.randh();
        log_H += -0.5*pow(m/1E3, 2);
    }
    else if(which == 1)
    {
        log_H -= -0.5*pow(b/1E3, 2);
        b += 1E3*rng.randh();
        log_H += -0.5*pow(b/1E3, 2);
    }
    else
    {
        // Usual log-uniform prior trick
        sigma = log(sigma);
        sigma += 20.*rng.randh();
        wrap(sigma, -10., 10.);
        sigma = exp(sigma);
    }

    // Calculate mu again if m or b changed
    if(which == 0 || which == 1)
        calculate_mu();

    return log_H;
}
\end{minted}

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[Caticha(2008)]{caticha} Caticha, A.\ 2008.\ Lectures 
on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
arXiv:0808.0012.

@@
